\chapter{Introduction}
Nowadays, automatic decision making is very important \cite{Lizheng2010}. An example of this is a Multi-agent system, which consists of multiple intelligent agents, computer-controlled players in an environment. These agents are controlled with automatic decision making. The purpose of this project is to develop an agent for the company Tygron. Tygron is a company that builds serious games for urban planning. Communities can generate and maintain realistic games to find solutions for city design and development projects. A game consists of a scenario in which several players play different roles, these players are real people. The goal of the virtual humans for serious gaming context project is to develop virtual humans that simulate the people in the Tygron game. Virtual humans can ensure that a serious game can be played even when not all players in the scenario are present. Each team in the project will develop one of these agents, so that we can run a simulation with only agents in the end. The agents have to behave as close as possible to a normal human playing the game. We want the agent to interact, think and behave in such a way that it is not recognizable for a human that he is playing with an agent.\\

The structure of this report is as follows:
In chapter 2, we give an overview of the developed and implemented software product. Chapter 3 consists of reflection on the product and process from a software engineering perspective. In chapter 4 the developed functionalities are described. Chapter 5 contains a special section on interaction design. In chapter 6 evaluation of the functional modules and the product in its entirety, including the failure analysis is given. In chapter 7 an outlook is given.
