\section{Competitors}
There are only a couple of products our product can compare against, and those products are the agents the other teams will write. But, because we just started on the project, the other teams haven't written their agents yet, so we cannot yet compete with them. This will obviously change when the project continues and at that point we will try to compare our agents against theirs to eventually optimize both of them. There is no documentation of the agents that were created during last years context project therefore we can’t compare our agent to the agents that we’re created before. Our agent will only work with the tygron engine and up to now the engine doesn’t have the ability to be used without each of the parties being controlled by a human. 
\par
Our product will make it possible to use the tygron engine without all the parties present. So that a single party can plan its features without the need for all other parties to be present. Of course this will only be an indicator as the agent might make different decisions than the person it replaces, but replacing the person representing the party with a different person would likely have the same effect. 
\par
Our agent will specifically represent The Delft University of Technology, this means it will act as an instance that want’s to keep its buildings up to date, while making sure that most of the students and all studies can be accommodated at all times. The agent will also want to make sure that all buildings can be easily reached by public transit.