\section{Addressing the customer needs}
When a session of the game is played it is possible that not all the stakeholders are currently present to take part in the game. Especially when the group of stakeholders is large it is hard to get them all together to play the game. To ensure that a serious session of the game can be played even when not all the stakeholders are present to take part, we need an agent or multiple agents to replace the roles of those stakeholders. 
\par
The main goal that the product aims to satisfy, is the possibility to replace one of the roles that are meant to be played by a human. This includes more than one thing. First of all, the agent that represents one of the roles present in a session of the game has to understand the needs of the represented stakeholder. The goal of the agent is to come to an understanding with the other stakeholders in a way that is optimal or close to optimal for the stakeholder that the agent replaces. To be able to do this, the agent is able to proficiently negotiate with the other players of the game. To be able to reach the best possible outcome for the represented stakeholders is not easy. There are multiple strategies for accomplishing results that are optimal for every user, but when negotiating with humans the results of these strategies vary.

\par
\textit{ “In essence, assumptions in most research are made that do not necessarily apply in genuine negotiations with humans, such as assuming complete information or the rationality of the opponent negotiator. In this sense, both parties are assumed to be rational in their behavior (for example, the decisions made by the agents are described as rational and the agents are considered to be expected utility maximizing agents that cannot deviate from their prescribed behavior). Yet, when dealing with human counterparts, one must take into consideration the fact that humans do not necessarily maximize expected utility or behave rationally. In particular, results from social sciences suggest that people do not follow equilibrium strategies.”}\cite{cacm}

\par
Our agents aim to be able to handle these kind of problems and come to an understanding with the other players of the game while optimizing the specified outcome for the stakeholder the agent is representing.
