\section{Contextual Inquiry}
In this section, the four principles of the contextual inquiry are described. The four principles are context, partnership, interpretation and focus.

\subsection{Context}
In this project, the Tygron Engine is the engine in which the agents should run. The first week was planned to get used to the engine. Knowing how the engine works, is important for the development of the agent. To achieve this knowledge, we visited Tygron in the first week for questions and explanation about the engine.  

\subsection{Partnership}
Because Tygron is the expert of the Tygron Engine, a weekly visit with Tygron is planned. This weekly meetings are planned for question, explanations and discussions. Working with people of Tygron is convenient for these questions, explanations and discussions. We prefer real interaction with the people working at Tygron above interaction with mail.

\subsection{Interpretation}
The avoid situation with wrong interpretations, communication is important. When question occur, the questions are asked to another group or Tygron. When we have another opinion about the answers of the question, we can discuss these face to face, which is mostly more beneficial in terms of time. 

\subsection{Focus}
Each visit with Tygron has its own focus. The focus for each visit is based on the problems and questions occurring in the week before the meeting. When the problems are discussed or solved, the focus will be replaced by another task of the sprint planning. 

